### 2020-11-10 doc/manuscript/Dow_manuscript.Rmd
title change

**Title:** Effect of spring temperatures on tree growth phenology in two temperate deciduous forests

>>>>

**Title:** ~~Effect of spring temperatures on tree growth phenology in two temperate deciduous forests~~
Warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little effect on annual woody productivity
